Water discharge has a variable impact on sediment transport capacity in subglacial systems

### 2023-08-11 Delaneyetal2023b.tex
Fig2 updated

    ianarburua.delaney@unil.ch},
  Daniel Farinotti\footnote{Laboratory of Hydraulics, Hydrology and Glaciology (VAW), ETH-Z\"urich, H\"onggerbergring 26, 8093 89 Z\"urich, Switzerland}$^{,}$\footnote{Swiss Federal Institute for Forest, Snow and Landscape Research (WSL) Z\"uricherstrasse 111, 8903 1011 Birmensdorf, Switzerland},
  Andrew J. Tedstone\footnote{Department of Geosciences, University of Fribourg, Ch. du Musée 1700, Fribourg, Switzerland},

@@

\subsection{Role of water discharge in sediment transport capacity}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{Fig2.pdf}
  \caption{Model outputs resulting from the hydrographs shown in panels a and e for the cases called \alpine (a-d) and \icesheet{} (e-h).". Gray (black) lines in a and e represent the subglacial channel size (water discharge).  In other panels, blue lines represent model outputs from the subglacial channel, while orange lines represent the subaerial channel.
    Data in plots are at $15$\unit{min} intervals.
    Arrows denote some events where the variable peaks in the subglacial channel prior to the subaerial one.
    Insets in e-h show peak events at the onset of melt in \icesheet{}.
    Note that the x and y axis are different for \alpine{} and \icesheet{} such that they each cover a summer.} 
  \label{fig:model_outs}
\end{figure}
Following the parameterizations defined in Sections~\ref{sect:sub_mode}~and~\ref{sect:fluv}, the water velocity, shear stress, and width-integrated shear stress exhibit different seasonal evolutions and peaks. Water velocity and shear stress represent the potential for sediment mobilization, and width-integrated shear stress represents the total sediment transport capacity across the channel bed (Figure~\ref{fig:model_outs}).

@@

Considerations in interpretations of sediment discharge should be made given the findings presented here.
These considerations include:
\begin{enumerate}
\item the inconsistent relationship between water discharge and sediment transport capacity underneath glaciers;
\item the timing of peak sediment transport capacity below glaciers can occur when the rate of change in water discharge is large, as opposed to the maximum quantity of water discharge;
\item the potentially increased variability in sediment discharge from underneath glaciers than in rivers they feed;
\item the multiple roles of water discharge to represent processes such as subglacial sediment transport capacity, subglacial sediment access, or open channel processes near the glacier margin in sediment records collected near glaciers. 
\end{enumerate}

>>>>

    ianarburua.delaney@unil.ch},
  Daniel Farinotti\footnote{Laboratory of Hydraulics, Hydrology and Glaciology (VAW), ETH-Z\"urich, H\"onggerbergring 26, 8093 89 Z\"urich, Switzerland}$^{,}$\footnote{Swiss Federal Institute for Forest, Snow and Landscape Research (WSL) Z\"uricherstrasse 111, 8903 1011 Birmensdorf, Switzerland},
  Andrew J. Tedstone\footnote{Department of Geosciences, University of Fribourg, Ch. du Musée 1700, Fribourg, Switzerland}

@@

\subsection{Role of water discharge in sediment transport capacity}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{Fig2.pdf}
  \caption{Model outputs resulting from the hydrographs shown in panels a and e for the cases called \alpine (a-d) and \icesheet{} (e-h).". Gray (black) lines in a and e represent the subglacial channel size (water discharge).  In other panels, blue lines represent model outputs from the subglacial channel, while orange lines represent the subaerial channel.
    Data in plots are at $15$\unit{min} intervals.
    Arrows denote some events where the variable peaks in the subglacial channel prior to the subaerial one.
    Insets in e-h show the  peak melt event \icesheet{} denoted by shaded area.
    Note that the x and y axis are different for \alpine{} and \icesheet{} such that they each cover a summer.} 
  \label{fig:model_outs}
\end{figure}
Following the parameterizations defined in Sections~\ref{sect:sub_mode}~and~\ref{sect:fluv}, the water velocity, shear stress, and width-integrated shear stress exhibit different seasonal evolutions and peaks. Water velocity and shear stress represent the potential for sediment mobilization, and width-integrated shear stress represents the total sediment transport capacity across the channel bed (Figure~\ref{fig:model_outs}).

@@

Considerations in interpretations of sediment discharge should be made given the findings presented here.
These considerations include:
\begin{enumerate}
\item the inconsistent relationship between water discharge and sediment transport capacity underneath glaciers;
\item the timing of peak sediment transport capacity below glaciers can occur when the rate of change in water discharge is large, as opposed to the maximum quantity of water discharge;
\item the potentially increased variability in sediment discharge from underneath glaciers than in rivers they feed;
\item the representations of water discharge such as subglacial sediment transport capacity, subglacial sediment access, or open channel processes near the glacier margin in sediment records collected near glaciers. 
\end{enumerate}
